\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\title{Some assumption and further explanations}
\author{Julia Hinrichs}

\section{Assumptions for CoCoME system}
In this section, I will describe some of my assumption in more detail and make it clear what I am mean with some definitions.
\subsection{Role: stock manager}
The stock manager is a role in the CoCoME system, which is mentioned in different use cases % link techreport
It is never clarified, which concrete tasks the stock manager has in the context of CoCoME. In my understanding following tasks and privileges this role inherits.
\begin{itemize}
\item The stock manager is a role in the context of a single store and manages the stock and the associated logistics for this store. Therefore, the role is only allowed to access the current and stock and the orders of all customer to forecast the needed products in the next time cycle. So use case 13 in the techreport doesn't make sense in this case.
\item the stock manager is for a whole enterprise responsible, this means for each store inside the enterprise. In this case the stock manager is responsible for all different stocks in the stores. The use case 13 in this scenario is interpreted as followed: \\


\section{Data types and roles}
Currently, the use case 13 is not implemented yet, so I am going to make some suggestions and assumption on how it will work in the future.
\end{itemize}
\end{document}